Logos Technologies builds autonomous drones that operate in a mission area independently to investigate targets of interest. Each drone uses automated target recognition and image projection to identify and localize areas of interest in real-time. During my two years at Logos Technologies, I was responsible for the development and deployment of algorithms in two domains: path planning and automated target recognition.\\

Path planning defines navigation behavior of where and how the drone moves in a given mission area. In global path-planning, the drone needs specific waypoints to navigate to a location while avoiding keep-out zones. I researched and implemented an improvement to the A* search algorithm, visibility graphs. In surveillance, the drone needs specific waypoints to navigate towards such that each area in a mission area gets visited occasionally, while high priority areas get visited more frequently. I researched and proposed a latency-graph representation of the problem, which provides an optimal route to minimize time between reacquiring areas of high priority. I also familiarized myself with motion planning, which uses convex optimization to find a desirable trajectory.\\

Automated target recognition is the algorithmic problem of recognizing targets of interest given image data. Convolutional neural networks are used ubiquitously due to the crucial translation-invariance property that the convolution function provides. I managed the Single-Shot-Detector (SSD), which uses a one-stage detection network to identify and localize targets. The network had a good detection accuracy of 90\% and ran at about 10 frames per second on an NVIDIA Xavier NX, but suffered from false alarms due to water glare. I implemented custom modifications to enable the network to run on low power embedded hardware. Later when the mission changed to allow for higher performance networks, I wrote data-loaders and modified the network architecture of RTDETR, allowing for higher performance in situatational contexts.\\

I provide details on all 4 path-planning algorithms that I have worked on in section 2, my work in automated target recognition in section 3, smaller projects that I worked on in section 4, and hobbyist projects that I worked on in my spare time in section 5. 